DOM Review Summary

### 2024-03-14 Analysis/ReviewSummary/ReviewSummary.qmd
Clean Study Details
Filtered down study details; started journals table

```{r prepare inputs}
#| include: false

library(tidyverse)
library(readxl)

@@

@@

@@

+---------------+-----------------------------------------------------------+-------------------------------------------------------------------------------------------------+
| Field         | Description                                               | Possible values                                                                                 |
+===============+===========================================================+=================================================================================================+
| Bayesian      | Whether the models fit were Bayesian                      | *Logical*                                                                                       |
+---------------+-----------------------------------------------------------+-------------------------------------------------------------------------------------------------+
| Prefiltering  | Which, if any, prefiltering method was used               | *Expert, Simple, Other*                                                                         |
+---------------+-----------------------------------------------------------+-------------------------------------------------------------------------------------------------+
| Selection     | Which, if any, selection method was used                  | *Single a priori, Multiple a priori, Exhaustive, Exhaustive by parameter, Forwards, Backwards*  |
+---------------+-----------------------------------------------------------+-------------------------------------------------------------------------------------------------+
| Evaluation    | How models were compared and evaluated                    | *AIC, AUC, DiC, Model-averaging, Bootstrapping*                                                 |
+---------------+-----------------------------------------------------------+-------------------------------------------------------------------------------------------------+
| Multi-species | Whether this was a multi-species model                    | *Logical*                                                                                       |
+---------------+-----------------------------------------------------------+-------------------------------------------------------------------------------------------------+
| Connectivity  | Whether site connectivity was incorporated into the model | *Logical*                                                                                       |
+---------------+-----------------------------------------------------------+-------------------------------------------------------------------------------------------------+

>>>>

```{r Load_packages}
#| include: false

library(tidyverse)
library(readxl)
library(knitr)
```

```{r Load_data}
#| include: false

@@

```{r StudyDetails_Clean}
#| include: false

studyDetails_clean <- review_StudyDetails |>
  filter(Status == "Complete")
```

@@

```{r StudyDetails_journals}
#| echo: false

studyDetails_clean |>
  summarise(Articles = n(), .by = "Journal") |>
  mutate(Journal = case_when(Articles == 1 ~ "Other",
                             .default = Journal)) |>
  summarise(Articles = sum(Articles), .by = "Journal") |> 
  arrange(-Articles) |>
  kable()
```

@@

+---------------+-----------------------------------------------------------+------------------------------------------------------------------------------------------------+
| Field         | Description                                               | Possible values                                                                                |
+===============+===========================================================+================================================================================================+
| Bayesian      | Whether the models fit were Bayesian                      | *Logical*                                                                                      |
+---------------+-----------------------------------------------------------+------------------------------------------------------------------------------------------------+
| Prefiltering  | Which, if any, prefiltering method was used               | *Expert, Simple, Other*                                                                        |
+---------------+-----------------------------------------------------------+------------------------------------------------------------------------------------------------+
| Selection     | Which, if any, selection method was used                  | *Single a priori, Multiple a priori, Exhaustive, Exhaustive by parameter, Forwards, Backwards* |
+---------------+-----------------------------------------------------------+------------------------------------------------------------------------------------------------+
| Evaluation    | How models were compared and evaluated                    | *AIC, AUC, DiC, Model-averaging, Bootstrapping*                                                |
+---------------+-----------------------------------------------------------+------------------------------------------------------------------------------------------------+
| Multi-species | Whether this was a multi-species model                    | *Logical*                                                                                      |
+---------------+-----------------------------------------------------------+------------------------------------------------------------------------------------------------+
| Connectivity  | Whether site connectivity was incorporated into the model | *Logical*                                                                                      |
+---------------+-----------------------------------------------------------+------------------------------------------------------------------------------------------------+
